{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-26 paper/paper.tex
corrected typo

This looks familiar to the \texttt{next} function we want to define.\footnote{We could define \texttt{next} for
every instruction $i$ inside an outermost branching point $[c]^n$ as $next(i) = jun(n)$.}. The part that is
missing, is the restriction to outermost branching points whose guards involves secrets.

>>>>

This looks familiar to the \texttt{next} function we want to define.\footnote{We could define \texttt{next} for
every instruction $i$ inside an outermost branching point $[c]^n$ as $next(i) = jun(n)$.} The part that is
missing, is the restriction to outermost branching points whose guards involves secrets.
